---
title: Coding Notes, Wrangle Concordances
author: mc
date: '2018-11-25'
slug: test
categories: []
tags: []
description: 'This script reads in a bunch of excel files of concordance lines in Spanish, aggregates them, and applies a custom function to trim the `left context` field, it specifically trims everything to the left of the last full stop. Plus it creates a top 10 ggplot bar graph!'
topics: []
type: 'post'
---

Test
<!--readmore--> 
#more

## Load the required packages
```{r}
library(dplyr, warn.conflicts = FALSE)
library(stringr)
library(readxl)
library(ggplot2)
```

## Get a list all of the excel files in the working directory
```{r}
file.list <- list.files(path = "datos_originales/", pattern='*.xlsx')
```

## Use paste to prefix the `datos_originales/` file path to each excel file (paste just preprends the first argument to the second argment
### https://stackoverflow.com/questions/6984796/how-to-paste-a-string-on-each-element-of-a-vector-of-strings-using-apply-in-r
```{r}
file.list.new <- paste("datos_originales/", file.list, sep="")
```

# Use lapply to apply read_excel() to every file in the working directory
```{r}
df.list <- lapply(file.list.new, read_excel)
```

```{r}
# Combine this into a data frame
df <- bind_rows(df.list)
```

# Data wrangle messy excel data

```{r}
# Some of the sheets had the cd column in a different order that's why we got cd one and cd two
colnames(df) <- c("izq","palabra","cd","der","cd2","encode","cd3")

# Rearrange columns
# Encode looks to be a repition of a cd column so don't select it
df <- df %>%
  select(izq, palabra, cd, cd2, cd3, der)

# Get a logical vector where the cd column is null
my.na <- is.na(df$cd)

# For those cases where cd column is null replace it with the cd2 column
df$cd[my.na] <- df$cd2[my.na]

# Repeat the same two steps above, now, where the cd column is STILL null replace it with cd3
my.na <- is.na(df$cd)
df$cd[my.na] <- df$cd3[my.na]

# Subset
df <- df %>%
  select(izq, palabra, cd, der)

# Cordance line to test function below
```


# Create custom recode function to trim concordances
```{r}
customRecode <- function(concordanceLine) {
  # Using the stringr package which is part of the tidy verse find all the
  # occurences of periods in the string
  listOfPeriods <- str_locate_all(concordanceLine, "\\.")
  
  # Get the length of the list of periods 
  getIndex <- length(listOfPeriods[[1]])
  
  # If there isn't a last period then just retrun the string how it is
  if (getIndex > 0) {
    
    # Use this length to pull the index of the period in the string
    indexOfLastPeriod <- listOfPeriods[[1]][getIndex]
    
    # Extract everything to the right of this string + 2 spaces
    newString <- str_sub(concordanceLine, start = indexOfLastPeriod + 2)
    
  } else {
    newString <- concordanceLine
  }
  
  return(newString)
}
```


# Use function to remove everything to the left of the last periord
```{r}
df$izqNew <- mapply(customRecode, df$izq)
```

# Re-arrange columns
```{r}
df <- df %>%
  select(izq, izqNew, palabra, cd, der)
```

# Remove duplicates, these must be from the duplicated sheets
```{r}
# See documetation below, part of tidyverse, it looks like you can specficy 
# columns or just pass in an entire data frame, I assume when you pass in an entire data frame
# every single row has to be the same
# http://www.datasciencemadesimple.com/remove-duplicate-rows-r-using-dplyr-distinct-function/
# https://www.rdocumentation.org/packages/dplyr/versions/0.7.6/topics/distinct
df <- distinct(df)
```
# Create a visualization of of the different counts
```{r}
# Get the top 10
df %>%
  count(palabra) %>%
  arrange(desc(n)) %>%
  top_n(10, n) %>%
  # See the reorder() solution
  # https://stackoverflow.com/questions/25664007/reorder-bars-in-geom-bar-ggplot2/25664367
  ggplot(aes(x = reorder(palabra, -n), y = n)) +
  geom_bar(stat="identity") +
  theme(text = element_text(size=20), axis.text.x = element_text(angle = 90)) +
  ggtitle("Top 10")
```


# Create a another dataframe to save the counts
```{r}
counts_of_df <- df %>%
  count(palabra) %>%
  arrange(desc(n))
```

# Save as excel
```{r}
# A Bit redundant, but it appears this package has to be used
# to write an excel file, other packages are problematic and rely
# and java dependencies.
# See here https://github.com/tidyverse/readxl/issues/231
library(openxlsx)

# Write the data as an xlsx file to the working directory
# The Tidyverse doesn't appear to have a writexl equivelant
openxlsx::write.xlsx(df, file = "datos.xlsx")
openxlsx::write.xlsx(counts_of_df, file = "conteo.xlsx")
```